Efficient Handling of String-Number Conversion

### 2020-03-31 final-version/evaluation.tex
debug

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{Leetcode}		& SAT      &  2501&  1721&  1898&   239 \\ 
								& UNSAT    & 16394& 15726& 16115& 15396 \\
								& UNKNOWN  &     0&     0&     0&   623 \\
								& TIMEOUT  &   32&  1480&   914&  2337 \\
								& ERROR    &     0&     0&     0&   332 \\
								& INCORRECT&     0&     0&     0&   108 \\ \hline 
\multirow{6}{*}{PythonLib}		& SAT      &   1922&   579&   914&   206 \\ 
								& UNSAT    &   724&   667&   724&   644 \\
								& UNKNOWN  &     0&     0&     0&    45 \\
								& TIMEOUT  &  0&  1400&  1008&  1710 \\
								& ERROR    &     0&     0&     0&    41 \\
								& INCORRECT&     0&     0&     0&     2 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &    20&     6&    16&     4 \\ 
								& UNSAT    &     0&     0&     0&     0 \\
								& TIMEOUT  &     0&    14&     4&    16 \\ \hline \hline
\multirow{6}{*}{Total}			& SAT      &  4443&  2306&  2828&   449 \\ 
								& UNSAT    & 17118& 16393& 16839& 16040 \\
								& UNKNOWN  &     0&     0&     0&   668 \\
								& TIMEOUT  &  32&  2894&  1926&  4063 \\
								& ERROR    &     0&     0&     0&   373 \\
								& INCORRECT&     0&     0&     0&   110 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
}
\end{table}

>>>>

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{Leetcode}		& SAT      &  2501&  1721&  1898&   239 \\ 
								& UNSAT    & 16394& 15726& 16115& 15288 \\
								& UNKNOWN  &     0&     0&     0&   623 \\
								& TIMEOUT  &   32&  1480&   914&  2337 \\
								& ERROR    &     0&     0&     0&   332 \\
								& INCORRECT&     0&     0&     0&   108 \\ \hline 
\multirow{6}{*}{PythonLib}		& SAT      &   1922&   579&   914&   206 \\ 
								& UNSAT    &   724&   667&   724&   642 \\
								& UNKNOWN  &     0&     0&     0&    45 \\
								& TIMEOUT  &  0&  1400&  1008&  1710 \\
								& ERROR    &     0&     0&     0&    41 \\
								& INCORRECT&     0&     0&     0&     2 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &    20&     6&    16&     4 \\ 
								& UNSAT    &     0&     0&     0&     0 \\
								& TIMEOUT  &     0&    14&     4&    16 \\ \hline \hline
\multirow{6}{*}{Total}			& SAT      &  4443&  2306&  2828&   449 \\ 
								& UNSAT    & 17118& 16393& 16839& 15930 \\
								& UNKNOWN  &     0&     0&     0&   668 \\
								& TIMEOUT  &  32&  2894&  1926&  4057 \\
								& ERROR    &     0&     0&     0&   379 \\
								& INCORRECT&     0&     0&     0&   110 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
}
\end{table}
